Proposal: Influences of GDP in the U.S

### 2022-10-07 Proposal/Proposal.tex
commit

\paragraph{Introduction}
%Introduction: Introducing the topic and why you have chosen this topic (3–5 lines). 
%Mention briefly the current related research and cite relevant works.
Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
It is a "comprehensive measure of U.S economic activity." \citet[]{gdp}
GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 
\citet{divya2014study} found that exchange rates and market indexes are important factors that influence an economies GDP. They also found that inflation is highly correlated, but not a significant influencer.

>>>>

\paragraph{Introduction}
%Introduction: Introducing the topic and why you have chosen this topic (3–5 lines). 
%Mention briefly the current related research and cite relevant works.
Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
It is a "comprehensive measure of U.S economic activity." \citet[]{bea}
GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 
\citet{divya2014study} found that exchange rates and market indexes are important factors that influence an economies GDP. They also found that inflation is highly correlated, but not a significant influencer.
